3. Analyses Plan

### 2021-06-30 analysis/reports/rmd/03_dataAnalyses.Rmd
prepare pre-registration

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

This report is the third in a series of reports covering this project. It reads the data prepared in the previous reports and analyzes them.

@@

>>>>

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

@@

[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/03_dataAnalyses.Rmd) is the third in a series of reports covering this project. It reads the data prepared in the previous reports and analyzes them.

@@

In addition to the summary statistics a regression table for each covariate as a dependent variable is needed. The independent variable will then be the data source (i.e. GMTV vs replication).
